Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-07-04 main.tex
Updates from Overleaf

\usepackage{xr-hyper}
\usepackage{hyperref}
%\newcommand{\R}[1]{\label{#1}\linelabel{#1}} % for \label page and line
\newcommand{\R}[1]{\linelabel{#1}} % for \label page and line
%\newcommand{\lr}[1]{page~\pageref{#1} (line~\lineref{#1})} % for \ref page and line
% for xr in your preamble
% https://www.overleaf.com/learn/how-to/Cross_referencing_with_the_xr_package_in_Overleaf
%\makeatletter
%\newcommand*{\addFileDependency}[1]{% argument=file name and extension
%  \typeout{(#1)}
%  \@addtofilelist{#1}
%  \IfFileExists{#1}{}{\typeout{No file #1.}}
%}
%\makeatother

@@

The candidate genes were validated by using the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}

@@

), GEPIA2021\cite{Li2021} (available at http://gepia2021.cancer-pku.cn/), or the Human Protein Atlas (HPA) website.

@@

Finally, these biomarkers were verified by using the gene expression profile from the GEO, HNSCC cell lines and tissues.\\

@@

The other investigators should get the rationale or revelation of the genes of interest on a specific cancer type. They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
SurvivaX.jsp\cite{Aguirre-Gamboa2013}, which has been lost since Oct/2019 and currently out of funds), and analyze the cohort (e.g., \acrshort{tcga}). After downloading the survival results, they could curate plots and tables carefully.
It is not possible to scan the whole human protein-coding genome in this way.
The web-based tools might set a cutoff at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses. There are several visualization software or R packages which deal with cutoff determination\cite{Abel1984}, %CRITLEVEL
such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/
packages/cutoffR). 
However, non of them could perform jointly predictive of survival times and cutoff selection within subgroups of gene expression.
%  %combine the scanning of the protein-coding genes and cutoff optimization programmatically.

%%% ***
In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial.
Our approach describes a workflow implemented in the R script, which runs on the Rstudio server.
Its function includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
The independent HNSCC datasets were used to validate this strategy.
The workflow, shown in Figure \ref{fig:figure1}, scanned 20,500 human protein-coding genes of the \acrshort{tcga} \acrshort{hnscc} cohort to yield a model with biomarker estimate.

@@

%When we increase the sample size, the standard error decrease
%, or increase the difference between the sample statistic and hypothesized parameter, the p value decreases, thus making it more likely that we reject the null hypothesis.
In a study with large sample size, the difference could be noticed easily (i.e., \textit{P} value $< 0.05$) due to a decreased standard error\cite{Sullivan2012}.
However, the small effect size (non-zero) is often meaningless or substantive insignificance.
%With a sufficiently large sample, a statistical test will always reveal a significant difference, unless the effect size is exactly zero.
%, that is, when the effect size is exactly zero; 
%yet very small differences, even if significant, are often meaningless. 
%Thus, reporting only the significant P value for an analysis is not adequate for readers to fully understand the results.
%If the magnitude of effect is small and clinically unimportant, the p-value can be "significant" if the sample size is large.
Conversely, the effect size can be large but fail to get statistical significance if the sample size is small. 
%In this scenario, the \textit{P} value tells the effect does not exist.
The following error could also impact the \textit{P} value:
\begin{outline}
\1 A random error, defined as the variability in data, is not considered a bias but rather occurs randomly across the entire study population and can distort the measurement process (e.g., RNA-Seq experiments).
The larger sample size could reduce the random error. 
\1 A systematic error is a bias, which includes selection bias, information bias, and confounding.
It could deleteriously impact the statistical significance.
The larger sample size could not affect the systematic error.
\end{outline}
% effect size is large (whatever is true or artificial), the p value is small
While statistical significance can inform the researcher whether an effect exists, the \textit{P} value will not directly tell the effect size.
Thus, if there is no error in two study groups, and the sample size is the same (not small), the group, which has a larger effect size, will has a small \textit{P} value\cite{Thiese2016}.
%The effect size is the main finding of a quantitative study.
If a skewed cutoff that split, for example, 425 versus 75 between the two groups, it will also get statistical significance by increasing effect size artificially.
% https://stats.stackexchange.com/questions/162359/how-can-you-have-p-0-0001-with-a-sample-size-of-89-and-a-control-group-of-52
%As you can see, even with only 12 events (fustat = 1) that split 10 vs 2 between the two dummy groups you get a log-rank p-value < 0.0001.
%effect size, sample size, cutoff 影響 p value!

@@

%2) \\
%(ok) % pvalueTex is essential; find smaller P value to predict large effect size (HR)
% The effect size is the main finding of a quantitative study.
There is a benefit for using sliding-window cutoff method (between $30\% - 70\%$ quantile) in Kaplan-Meier analysis of TCGA HNSCC cohort at the beginning.
We compared the results of cutoff at optimal \textit{P} value by sliding window or just at the median of gene expression.
It shows that the number of genes with unadjusted \textit{P} value $< 0.05$, which is 6284 versus 3118, respectively. After FDR correction, it becomes 967 versus 209, respectively.
% HNSCC_OS_marginS_THREE_pvalue005_noCancerGene
%Result by optimal cutoff: total 9416 plots,
%6284 are raw KM P value < 0.05
%534?? genes are FDR KM P value <0.05
%967 genes which HR is greater than 1.5 or less than 0.5.
%Result by median cutoff: total 20080 genes, 
%3118 are raw KM P value < 0.05; 
%209 genes are FDR KM P value <0.05
The sliding-window cutoff method could catch more potential candidates, which have \textit{P} values far less than $0.001$, for subsequent Cox's modeling.
That is because of the properly selected cutoff improving the statistical significance.
To find a smaller \textit{P} value might predict large effect size (HR) associated biomarkers.
Then, these preliminary candidates will have an opportunity to be carefully selected by using Bonferroni correction, their effect size (Cox's HR), and the other independent cohort (GSE65858) to prevent the false discovery.
% no more GSE2837
%small effect size could be double-checked by GSE65858.
%差別很大，張大網
%([2021/06/27] run code: if median cut for TCGA KM Cox by *** pvalueTex code)
%列入 workflow in materials and methods;

@@

The other example is IL19. It has a \textit{P} value plot with acute S-curve bending at the median zone, that lets the FDR-adjusted \textit{P} value has large difference between 50\% quantile cutoff (FDR 0.115) and optimal 48\% quantile cutoff (FDR \num{6.54e-6}). This optimal cutoff method could boost it's statistic significance to pass the correction by both FDR and Bonferroni methods. However, IL19 has competed as a candidate by its effect size (HR = 0.472 in TCGA cohort), but failed by the validation with GSE65858 cohort (HR = 0.630 and FDR-KM \textit{P} = 0.031).

@@

%\subsubsection{HPA} %still TCGA's RNA-Seq
The Human Protein Atlas project (HPA) has proteomics analysis based on 26,941 antibodies targeting 17,165 unique proteins. The HPA's Pathology Atlas analyzes each protein in patients, using \acrshort{ihc} analysis based on tissue microarrays (TMAs) adopted from TCGA. Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
All transcriptomic data were retrieved from the TCGA, and all proteomics were generated in-house using the same antibodies.
The genes (e.g. CAMK2N1, and NDFIP1) are also on the list of unfavorable prognostic genes for HNSCC from \acrshort{hpa} (available at https://www.proteinatlas.org/\\humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19). 
FCGBP is on the list of favorable prognostic genes as well.
% DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, and DKC1
% ZNF557, ZNF266, and FCGBP
%Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level (HPA database, available at https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer)\cite{Ren2020}.
% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
%found at Human Protein Atlas dataset 
%(Please see Supplementary Figure S3)%\ref{fig:fig_HPA_USP10})
% moved to Supplementary

@@

% in coverletter
% line \ref{line_fr:answer1-2} ~ \ref{line_to:answer1-2} of page %\pageref{page_fr:answer1-2}, \pageref{page_to:answer1-2}
% in main.tex
% %\label{page_fr:answer1-2}, \label{page_to:answer1-2}
% \linelabel{line_fr:answer1-2} , \linelabel{line_to:answer1-2}
%****************%
\subsubsection{Holistic Cancer Care} 
\R{from:answer1-2}
%\linelabel{line_fr:answer1-2}

@@

\R{to:answer1-2}
%\label{page_to:answer1-2} % page number
%\linelabel{line_to:answer1-2} % line number
% \label{line_to:answer1-2} % section number

@@

$h(t) = h_0(t) \times exp(\beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n)$\\[0.3cm]
% natural exponential function => y=e^x
\end{flushleft}
where,\\
\begin{outline} % for highlight
\1 t represents the survival time;
\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g., clinicopathological features, including age, gender, gene expression, cancer stage, smoking, alcohol, spiritual, emotional, and social status;
\1 The coefficients ($\beta_1...\beta_n$) measure the impact---the effect size of covariates;
\1 The term $h_0$ is called the baseline hazard. It corresponds to the hazard value if all the $X_i$ are equal to zero. The "t" in $h(t)$ indicates the hazard may vary over time.
\end{outline}

@@

\begin{MyColorPar}{red}
GSE65858 is a dataset for candidate selection in our workflow.
The Gene Expression Omnibus (GEO) database\cite{Chung2006},, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data,  including microarray and sequence-based experiments.
R package of GEOquery\cite{Sean2007} was used to
download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
GSE65858\cite{Wichmann2015} has OS event, RFS event, and survival time.
There are 270 HNSCC participants involved in this cohort.
%The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30,330.
%n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on 7 November, 2009). % (RefSeq) 
GSE65858 is a dataset for helping of candidate selection in our workflow.
We have also performed Kaplan-Meier and Cox survival analyses under the cutoff of each gene expression at their median value.
\end{MyColorPar} % red

>>>>

%\usepackage{xr-hyper}
\usepackage{hyperref}
%\newcommand{\R}[1]{\label{#1}\linelabel{#1}} % for \label page and line
%\newcommand{\R}[1]{\linelabel{#1}} % for \label page and line
%\newcommand{\lr}[1]{page~\pageref{#1} (line~\lineref{#1})} % for \ref page and line
% for xr in your preamble
% https://www.overleaf.com/learn/how-to/Cross_referencing_with_the_xr_package_in_Overleaf
%\makeatletter
%\newcommand*{\addFileDependency}[1]{% argument=file name and extension
%  \typeout{(#1)}
%  \@addtofilelist{#1}
%  \IfFileExists{#1}{}{\typeout{No file #1.}}
%}
%\makeatother

@@

They validated their candidate genes by using the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}

@@

), GEPIA2021\cite{Li2021} (available at http://gepia2021.cancer-pku.cn/), and the web-tools: Human protein atlas (HPA)\cite{Uhlen2017} (please also see the Discussions section "Validation by Web-based Tools" in this article).

@@

Finally, their biomarkers were verified by using the gene expression profile from the GEO, HNSCC cell lines and tissues.\\

@@

The other investigators should get the rationale or revelation of the genes of interest on a specific cancer type. They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
SurvivaX.jsp\cite{Aguirre-Gamboa2013}, which has been lost since Oct/2019 and currently out of funds), and analyze the cohort (e.g., \acrshort{tcga}). After downloading the survival results, they could curate plots and tables carefully.
It is not possible to scan the whole human protein-coding genome in this way.
The web-based tools might set a cutoff at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses. There are several visualization software or R packages which deal with cutoff determination\cite{Abel1984}, %CRITLEVEL
such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/
packages/cutoffR). 
However, non of them could perform jointly predictive of survival times and cutoff selection within subgroups of gene expression.
%  %combine the scanning of the protein-coding genes and cutoff optimization programmatically.

%%% ***
In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial.
Our approach describes an in-house workflow implemented in the R script, which runs on the Rstudio server.
Its function includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
The independent HNSCC dataset (GSE65858) was used to validate this strategy.
The workflow, shown in Figure \ref{fig:figure1}, scanned 20,500 human protein-coding genes of the \acrshort{tcga} \acrshort{hnscc} cohort to yield a model with biomarker estimate.

@@

%When we increase the sample size, the standard error decrease
%, or increase the difference between the sample statistic and hypothesized parameter, the p value decreases, thus making it more likely that we reject the null hypothesis.
In a study with large sample size, the difference could be noticed easily (i.e., \textit{P} value $< 0.05$) due to a decreased standard error\cite{Sullivan2012}.
However, the small effect size (non-zero) is often meaningless or substantive insignificance (e.g., hazard ratio between 0.8 and 1.2).
%With a sufficiently large sample, a statistical test will always reveal a significant difference, unless the effect size is exactly zero.
%, that is, when the effect size is exactly zero; 
%yet very small differences, even if significant, are often meaningless. 
%Thus, reporting only the significant P value for an analysis is not adequate for readers to fully understand the results.
%If the magnitude of effect is small and clinically unimportant, the p-value can be "significant" if the sample size is large.
Conversely, the effect size can be large but fail to get statistical significance if the sample size is small. 
%In this scenario, the \textit{P} value tells the effect does not exist.
The following error could also impact the \textit{P} value:
\begin{outline}
\1 A random error, defined as the variability in data, is not considered a bias but rather occurs randomly across the entire study population and can distort the measurement process (e.g., RNA-Seq experiments).
The larger sample size could reduce the random error. 
\1 A systematic error is a bias, which includes selection bias, information bias, and confounding.
It could deleteriously impact the statistical significance.
The larger sample size could not affect the systematic error.
\end{outline}
% effect size is large (whatever is true or artificial), the p value is small
While statistical significance can inform the researcher whether an effect exists, the \textit{P} value will not directly tell the effect size.
Thus, if there is no error in two study groups, and the sample size is the same (not small), the group, which has a larger effect size, will has a small \textit{P} value\cite{Thiese2016}.
%The effect size is the main finding of a quantitative study.
If a skewed cutoff that split, for example, 425 versus 75 between the two groups, it will also get statistical significance by increasing effect size artificially.
% https://stats.stackexchange.com/questions/162359/how-can-you-have-p-0-0001-with-a-sample-size-of-89-and-a-control-group-of-52
%As you can see, even with only 12 events (fustat = 1) that split 10 vs 2 between the two dummy groups you get a log-rank p-value < 0.0001.
%effect size, sample size, cutoff 影響 p value!

@@

%2) \\
%(ok) % pvalueTex is essential; find smaller P value to predict large effect size (HR)
% The effect size is the main finding of a quantitative study.
There is a benefit for using sliding-window cutoff method (between $30\% - 70\%$ quantile) in Kaplan-Meier analysis of TCGA HNSCC cohort at the beginning.
We compared the results of cutoff at optimal \textit{P} value by sliding window or just at the median of gene expression.
It shows that the number of genes (with unadjusted \textit{P} value $< 0.05$)  is 6284 versus 3118, respectively. After FDR correction, it becomes 967 versus 209, respectively.
% HNSCC_OS_marginS_THREE_pvalue005_noCancerGene
%Result by optimal cutoff: total 9416 plots,
%6284 are raw KM P value < 0.05
%534?? genes are FDR KM P value <0.05
%967 genes which HR is greater than 1.5 or less than 0.5.
%Result by median cutoff: total 20080 genes, 
%3118 are raw KM P value < 0.05; 
%209 genes are FDR KM P value <0.05
The sliding-window cutoff method could catch more potential candidates, which have \textit{P} values far less than $0.001$, for subsequent Cox's modeling.
That is because of the properly selected cutoff improving the statistical significance.
To find a smaller \textit{P} value might predict large effect size (HR) associated biomarkers.
Then, these preliminary candidates will have an opportunity to be carefully selected by using FDR then stringent Bonferroni correction, their effect size (Cox's HR), and the other independent cohort (GSE65858) to prevent the false discovery.
% no more GSE2837
%small effect size could be double-checked by GSE65858.
%差別很大，張大網
%([2021/06/27] run code: if median cut for TCGA KM Cox by *** pvalueTex code)
%列入 workflow in materials and methods;

@@

The other example is IL19. It has a \textit{P} value plot with acute S-curve bending at the median zone, that lets the FDR-adjusted \textit{P} value has large difference between 50\% quantile cutoff (FDR 0.115) and optimal 48\% quantile cutoff (FDR \num{6.54e-6}). This optimal cutoff method could boost it's statistic significance to pass the correction by both FDR and Bonferroni methods. Even IL19 has competed as a candidate by its effect size (HR = 0.472 in TCGA cohort), but failed by the validation with GSE65858 cohort (HR = 0.630 and FDR-KM \textit{P} = 0.031).

@@

%\subsubsection{HPA} %still TCGA's RNA-Seq
The Human Protein Atlas project (HPA) has proteomics analysis based on 26,941 antibodies targeting 17,165 unique proteins. The HPA's Pathology Atlas analyzes each protein in patients, using \acrshort{ihc} analysis based on tissue microarrays (TMAs) adopted from TCGA. Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
All transcriptomic data were retrieved from the TCGA, and all proteomics were generated in-house using the same antibodies.
The our candidate, CAMK2N1, is also on the list of unfavorable prognostic genes for HNSCC from \acrshort{hpa} (available at https://www.proteinatlas.org/\\humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19). 
CALML5 and FCGBP are on the list of favorable prognostic genes as well.
% DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, and DKC1
% ZNF557, ZNF266, and FCGBP
%Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level (HPA database, available at https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer)\cite{Ren2020}.
% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
%found at Human Protein Atlas dataset 
%(Please see Supplementary Figure S3)%\ref{fig:fig_HPA_USP10})
% moved to Supplementary

@@

% in coverletter
% line \ref{line_fr:answer1-2} ~ \ref{line_to:answer1-2} of page %\pageref{page_fr:answer1-2}, \pageref{page_to:answer1-2}
% in main.tex
% %\label{page_fr:answer1-2}, \label{page_to:answer1-2}
% \linelabel{line_fr:answer1-2} , \linelabel{line_to:answer1-2}
%****************%
\subsubsection{Holistic Cancer Care} 
%\R{from:answer1-2}
%\linelabel{line_fr:answer1-2}

@@

%\R{to:answer1-2}
%\label{page_to:answer1-2} % page number
%\linelabel{line_to:answer1-2} % line number
% \label{line_to:answer1-2} % section number

@@

$h(t) = h_0(t) \times exp(\beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n)$\\[0.3cm]
% natural exponential function => y=e^x
\end{flushleft}
where,\\
\begin{outline} % for highlight
\1 t represents the survival time;
\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g., clinicopathological features, including age, gender, gene expression, cancer stage (tumor size, nodal metastasis, distant metastasis), surgical margin, smoking, and alcohol; unfortunately, spiritual, emotional, and social status are not available in TCGA database;
\1 The coefficients ($\beta_1...\beta_n$) measure the impact---the effect size of covariates;
\1 The term $h_0$ is called the baseline hazard. It corresponds to the hazard value if all the $X_i$ are equal to zero. The "t" in $h(t)$ indicates the hazard may vary over time.
\end{outline}

@@

\begin{MyColorPar}{red}
GSE65858 is a dataset for candidate selection in our workflow.
The Gene Expression Omnibus (GEO) database\cite{Chung2006},, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data,  including microarray and sequence-based experiments.
R package of GEOquery\cite{Sean2007} was used to
download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
GSE65858\cite{Wichmann2015} has OS event, RFS event, and survival time.
There are 270 HNSCC participants involved in this cohort.
%The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30,330.
%n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on 7 November, 2009). % (RefSeq) 
GSE65858 is a dataset for helping of candidate selection in our workflow.
We have also performed Kaplan-Meier (with FDR-correction of \textit{P} value) and Cox survival analyses under the cutoff of each gene expression at their median value.
\end{MyColorPar} % red
